%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{sawyer}{hopkins}{fullstack engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Los Gatos, CA
~
\href{mailto:sawyer@sawyerhopkins.com}{sawyer@sawyerhopkins.com}
\href{http://www.sawyerhopkins.com}{www.sawyerhopkins.com}
\section{programming}
{\color{red} $\varheartsuit$} JavaScript / NodeJS
Vue, React, Redux
Jest, Sinon
\section{tech}
Docker
AWS / Cloudformation
Serverless
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2014--2017}
{Masters {\normalfont in Physics}}
{Kansas State University}
{\begin{itemize}
\item Performed stochastic n-body dynamical simulations using software built using C++.
\item Modeled phase space of protein solutions under the effects of non-pairwise electrostatic interactions.
\end{itemize}}

%------------------------------------------------

\entry
{2010--2014}
{Bachelor {\normalfont in Physics}}
{Michigan Technological University}
{\begin{itemize}
\item Studied nanotechnology with a focus on thermal properties of boron nitride nanosheets.
\item Operated vapour deposition chambers for experimental synthesis of nanostructures.
\end{itemize}}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}

\entry
{2018-Now}
{Radiowave.io}
{Manhattan, KS}
{\emph{Lead Javascript Engineer} \\
\begin{itemize}
\item Managing infrastructure as code using AWS Cloudformation.
\item Developing progressive web applications using Nuxt.
\item Creating real-time stream metrics, data visualization, and reports for radio broadcasters.
\end{itemize}}

\entry
{2017-Now}
{Import.io}
{Los Gatos, CA}
{\emph{Fullstack Engineer} \\
\begin{itemize}
\item Utilizing headless chromium to convert unstructured HTML into machine readable formats (JSON, CSV).
\item Orchestrating complex micro-service workflows using technologies such as SQS, SNS, Redis, and SWF.
\item Integrating data pipelines with mechanical turk for statistically sampled quality metrics.
\end{itemize}}

\entry
{2015-2017}
{Piestar}
{Manhattan, Kansas}
{\emph{Web Developer} \\
\begin{itemize}
\item Creating single page applications using modern javascript technologies including React and Vue.js.
\item Designing and implementing restful API endpoints using PHP and Laravel.
\end{itemize}}

\end{entrylist}

\end{document}